\chapter*{Acknowledgements}
% It doesn't really matter in which order the acknowledgements and abstract come.
% In some ways it's nice to put the acknowledgements first then everything that follows is about the project you have done.

% You should generally thank your supervisor(s) in your acknowledgements
% --- not doing so makes quite a statement.
Primarily, I want to thank my supervisors Dr. Timon Gutleb and Prof. José Carrillo for their valuable support in the research and writing process of this dissertation.
Timon's expertise and joy for numerical methods and their application is truly inspiring and I wish him the best for all his future endeavours, especially in his new role as a father!
I would like to extend further gratitude to our course director, Dr. Kathryn Gillow, for her never-ending support to all of us throughout the course.
% If anyone else has helped with the project then thank them too.
I also want to thank my departmental and college supervisors, Prof. Yuji Nakatsukasa and Dr. Jani Bolla for their steadily positive influence, contagious excitement and good advice.
I am grateful to my friend Fredrik Meisingseth for his helpful comments on the written parts.

% If you have received funding from anywhere, it is standard to thank your funding body.
I would like to thank the Steirische Stipendienstiftung for their generous support which enabled me to pursue this degree in the first place.
Of course I also want to thank my girlfriend Hanna, family and friends who have always been there for me.
Among these are course mates on the MMSC and friends from Wolfson that really made this year so much more enjoyable.
With greatest respect and in no particular order, I especially want to thank Jad, Lucas, Adam, Emilie, Mitja, Nicholas, Ben, Luna, Jacob, Kirschi, Mira, Satya, Atticus, Elias, Sam and Madhu.

% It's then up to you who else to thank. You can be brief and stop there, or you can thank family, friends, cohort.

% - eventually a cool quote
