\chapter{Particle Interaction Theory}
\label{chap:particle-interaction-theory}

\input{chapters/out/Particle Interaction Theory.md.tex}

\section{Self-Propulsion}
Makes it active matter.

Self-propulsion and friction could be modelled as a quadratic of the form
$$f(v_i) = 1.6 - 0.5 v_i^2\,,$$
where $v_i := \norm{\vec{v_i}} = \norm{\frac{\dd\vec{x_i}}{\ddt}}$.
Show reproduced plots from \cite{2006-self-propelled}.

\section{Kinetic Theory: The Vlasov Equation}
A very common tool in Plasma physics.
$$\frac{\partial f}{\partial t}+{\frac {\mathrm {d} \mathbf {r} }{\mathrm {d} t}}\cdot {\frac {\partial f}{\partial \mathbf {r} }}+{\frac {\mathrm {d} \mathbf {p} }{\mathrm {d} t}}\cdot {\frac {\partial f}{\partial \mathbf {p} }}=0,$$

This is the collisionless Boltzmann equation.
Vlasov replaces the collision term with long-range interactions.

\begin{theorem}{Liouville's}{liouville}
  Says that phase-space volume is conserved in situations of a pure particle-particle interaction.
  $$\frac{d\rho}{dt}=
    \frac{\partial\rho}{\partial t}
    +\sum_{i=1}^n\left(\frac{\partial\rho}{\partial q_i}\dot{q}_i
    +\frac{\partial\rho}{\partial p_i}\dot{p}_i\right)=0\,.$$
\end{theorem}

\section{Vicsek Model}
For the study of active matter (a number of individual agents).

\section{Swarming}
A 2010 paper by \citeauthor{2010-starlings} showed the surprising result that correlation between movement of individual starlings in bird flocks over Rome is scale-free.
In contrast to the assumption that birds only mirror their neighbours' behaviour and swarming behaviour emerges as a result of that, this observation suggests that bird flocks exert collective behaviour beyond local interactions.
\begin{quote}
  The change in the behavioral state of one animal affects and is affected by that of all other animals in the group, no matter how large the group is
  \parencite{2010-starlings}.
\end{quote}
This work was done by individually tracking each starling in the flock and using tracking algorithms to represent their 3 dimensional positions and velocities.
